MSF_Groupwork-NBA_shotlog

### 2016-10-16 MSFGroupwork-NBAHotHand.Rmd
Table 13 added

###Plot Result
  The explanation from the plot above are as follows. The shooter distance ranges and accuracy:   
  1.  0 to 2 feet: the accuracy varied between **62%** to **68%**  
  2.  2 to 4 feet: the accuracy rate for this distance range from **61%** to **67%**  
  3.  4 to 6 feet: the accuracy rate for this distance range from **44%** to **58%**  
  4.  6 to 8 feet: the accuracy rate for this distance range from **38%** to **51%**  
  5.  8 to 10 feet: the accuracy rate for this distance range from **35%** to **42%**  
  6.  10 to 12 feet: the accuracy rate for this distance range from **34%** to **42%**  
  7.  12 to 14 feet: the accuracy rate for this distance range from **37%** to **47%**  
  8.  14 to 16 feet: the accuracy rate for this distance range from **33%** to **51%**  
  9.  16 to 18 feet: the accuracy rate for this distance range from **37%** to **48%**  
  10. 18 to 24 feet: the accuracy rate for this distance range from **33%** to **43%**  
  11. 24 to 28 feet: the accuracy rate for this distance range from **18%** to **38%**  
  12. more than 28 feet: the accuracy varies greater than previous distance range, starting from **0%** (no shots scored from that distance) to **50%**

>>>>

###Plot Result

**Table 13**: The relationship between the shooter distance ranges and accuracy

  Distance (in feet) | Accuracy (range in %)
  - | -
  0 - 2 | 62 - 68
  2 - 4 | 61 - 67
  4 - 6 | 44 - 58
  6 - 8 | 38 - 51
  8 - 10 | 35 - 42
  10 - 12 | 34 - 42
  12 - 14 | 37 - 47
  14 - 16 | 33 - 51
  16 - 18 | 37 - 48
  18 - 24 | 33 - 43
  24 - 28 | 18 - 38
  28+ | 0 - 50
